### 2019-09-17 2019_neurips_vigil/model.tex
Updated model section. Cosmetic changes to other sections.

\begin{figure}[hbtp]
	\centering
	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
	\caption{General architecture of SAMNet}
	\label{fig:samnet}
\end{figure}

@@

\begin{figure}[hbtp]
	\centering
	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
	\caption{Single reasoning step in SAMCell}
	\label{fig:samcell}
\end{figure}

@@

\paragraph{Question-driven Controller.}

%The Question-driven Controller plays an important role in the reasoning process.
%It drives the attention over the question and produces the new control states. Each new control state defines a new reasoning operation. The inputs of this unit are the past control state, the question encoding and the contextual words (see Question Encoding Unit). It uses the dot product attention between the contextual words
%and the combination of the past control states and the question encoding.  This attention layer produces the new control state.
%
%This unit also outputs the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words (last, latest, now, none temporal).

This module drives attention over the question to produce $k$ control states, one per reasoning operation. 
The control state $c_t$ at step $t$ is then fed to temporal classifier, a two-layer feedforward network with ELU activation in the hidden layer of $d$ units.
The output $\tau_t$ of the classifier is intended to represent the different temporal contexts (or lack thereof) associated with the word in focus for that step of reasoning.	
For example in case of the COG dataset we pick 4 classes to capture the terms labeled ``last'', ``latest'', ``now'', and ``none''.

The visual (resp. memory) retrieval unit uses the information generated above to extract a relevant object from the frame (resp. memory)
along with an attention vector over the feature vectors of that frame (resp. over memory addresses). Note that the returned object may not be valid, 
e.g., if the current reasoning step focuses on the phrase ``last red square'', the returned object from the current frame
will be invalid even if it contains a red square. The attention vector over the memory $rh_t$ is also called the \emph{read head} since it will be used 
for memory updates later.

\paragraph{Reasoning Unit}
This module is the backbone of SamNet that determines what gating operations need to be performed on the external memory, postponing the actual updates
themselves to the memory update unit. It also determines whether the relevant object for reasoning is supposed to be retrieved from the current frame or from external memory.

@@

\paragraph{Memory Update Unit.}

%# get attention on the correct slot in memory based on the 2 predicates
%# attention defaults to 0 if neither condition holds
%wt = do_replace * read_head + do_add_new * write_head
%
%# Update visual_working_memory
%new_visual_working_memory = (visual_working_memory * (1 - wt)[..., None]
%+ wt[..., None] * visual_object[..., None, :])
%
%# compute shifted sequential head to right
%shifted_write_head = torch.roll(write_head, shifts=1, dims=-1)
%
%# new sequential attention
%new_write_head = ((shifted_write_head * do_add_new)
%+ (write_head * (1 - do_add_new)))

TO BE WRITTEN

The  Summary Unit is the last unit of the SAM Cell. It is responsible to output the new summary object. It first picks which object is relevant between the object extracted from memory and the visual object extracted from the image. Once the relevant object is picked, it is combined with the former summary object through a linear layer to become the new summary object. It is the final step of the SAM Cell reasoning cycle.

The details of the modules image encoder, question encoder and output unit are described in the appendix.

>>>>

\begin{wrapfigure}{R}{0.8\textwidth}
	\centering
	\includegraphics[width=0.78\textwidth]{../img/architecture/samnet_architecture4}
	\caption{General architecture of SAMNet}
	\label{fig:samnet}
\end{wrapfigure}

%\begin{figure}[hbtp]
%	\centering
%	\includegraphics[width=0.7\textwidth]{../img/architecture/samnet_architecture4}
%	\caption{General architecture of SAMNet}
%	\label{fig:samnet}
%\end{figure}

@@

\begin{wrapfigure}{R}{0.8\textwidth}
	\centering
	\includegraphics[width=0.78\textwidth]{../img/architecture/samcell_reasoning}
	\caption{Single reasoning step in SAMCell}
	\label{fig:samcell}
\end{wrapfigure}

%\begin{figure}[hbtp]
%	\centering
%	\includegraphics[width=0.7\textwidth]{../img/architecture/samcell_reasoning}
%	\caption{Single reasoning step in SAMCell}
%	\label{fig:samcell}
%\end{figure}

@@

\noindent{\textbf{Question-driven Controller.}}
This module drives attention over the question to produce $k$ control states, one per reasoning operation. 
The control state $c_t$ at step $t$ is then fed to temporal classifier, a two-layer feedforward network with ELU activation in the hidden layer of $d$ units.
The output $\tau_t$ of the classifier is intended to represent the different temporal contexts (or lack thereof) associated with the word in focus for that step of reasoning.	
For example in case of the COG dataset we pick 4 classes to capture the terms labeled ``last'', ``latest'', ``now'', and ``none''.

The visual (resp. memory) retrieval unit uses the information generated above to extract a relevant object $vo_t$ from the frame (resp. $mo_t$ from memory)
along with an attention vector over the feature vectors of that frame (resp. over memory addresses). Note that the returned object may not be valid, 
e.g., if the current reasoning step focuses on the phrase ``last red square'', the returned object from the current frame
will be invalid even if it contains a red square. The attention vector over the memory $rh_t$ is also called the \emph{read head} since it will be used 
for memory updates later.

\noindent{\textbf{Reasoning Unit.}}
%\paragraph{Reasoning Unit.}
This module is the backbone of SamNet that determines what gating operations need to be performed on the external memory, postponing the actual updates
themselves to the memory update unit. It also determines whether the relevant object for reasoning is supposed to be retrieved from the current frame or from external memory.

@@

\noindent{\textbf{Memory Update Unit.}}
We first determine the exact location where an object could be added to the memory using the following equation:
\[ w_t = \doreplace \cdot \rhead_t + \doadd \cdot \whead_{t-1} \]
Above, $w_t$ denotes the pseudo-attention vector that represents the ``location'' where the memory update should happen.
The sum of components of $w$ is at most equal to 1; and $w_t$ can even equal 0 whenever neither condition
of adding a new object nor replacing an existing object holds true.
We then update the memory accordingly as:
\[ M_t = M_{t-1} \odot (J - w_t \otimes \mathbf{1}) + w_t \otimes vo_t,\]
where $vo_t$ denotes the object returned by the visual retrieval unit. 
Here $J$ denotes the all ones matrix, $\odot$ denotes the Hadamard product and $\otimes$ denotes the Kronecker product. 
Note that the memory is unchanged in the case where $w_t = 0$, i.e., $M_t = M_{t-1}$.
We finally update the write head so that it points to the succeeding address if an object was added to memory or otherwise stay the same.
Let $\whead'_{t-1}$ denote the circular shift to the right of $\whead_{t-1}$ which corresponds to the soft version of this operation.
Then we update the write head according to the equation:
\[ \whead_t = \doadd \cdot \whead'_{t-1} + (1-\doadd) \cdot \whead_{t-1} \]

\noindent{\textbf{Summary Update Unit.}}
%\paragraph{Summary Update Unit.}
This unit updates the summary object to be the outcome of the $t$-th reasoning step.
We first determine whether the relevant object $ro_t$ should be obtained from memory or the frame according to:
\[ ro_t = \imatch_t \cdot vo_t + \mmatch_t \cdot mo_t \]
Note that $ro_t$ could be a null object (i.e. 0 vector) in case neither of the gates evaluate to true.
Finally, $so_t$ is the output of a simple linear layer whose inputs are $ro_t$ and the previous summary object $so_{t-1}$.
This serves to retain additional information that was in $so_{t-1}$, e.g., if it held the partial result of a complex query with Boolean connectives.

For more details of the various modules, please see the appendix.
